Comb associative operads

### 2018-07-09 Operads_rewrite.tex
Modification algo de Buchberger v2

When $\Rew$ is a terminating but not convergent orientation of $\Congr$,
we shall use a variant of the \Def{Buchberger semi-algorithm} for
operads~\cite[Section 3.7]{DK10} to compute a set of rewrite rules
$\Rew'$ such that, as binary relations $\Rew \subseteq \Rew'$, and
$\Rew'$ is a convergent orientation of $\Congr$. This semi-algorithm
takes as input a finite set of rewrite rules $\Rew$ and outputs the set
of rewrite rules $\Rew'$ satisfying the property stated above. Here is,
step by step, a description of its execution:
\begin{enumerate}[label={(\it\arabic*)}]
\item Set $\Rew' := \Rew$ and let $\BranchingTrees$ be the set of
  branching trees for $\RewContext$.
\item \label{item:loop_start_buchberger}
  If $\BranchingTrees$ is empty, the execution stops and the output
  is $\Rew'$.
\item Otherwise, let $\Tfr$ be the branching tree for $\RewContext'$
  with the minimal degree and the minimal prefix word and remove $\Tfr$
  from $\BranchingTrees$.
\item Let $\{\Sfr_1, \Sfr_2\}$ be the branching pair for $\Tfr$ such
  that $\Sfr_1$ and $\Sfr_2$ have the minimal prefix words.
\item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be normal forms of
  $\Sfr_1$ and $\Sfr_2$, respectively.
\item If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
  to $\Rew'$ the rewrite rule
    \begin{math}
      \max_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}
      \Rew'
      \min_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}.
    \end{math}
  \item Go to Step~\ref{item:loop_start_buchberger}.
\end{enumerate}
The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is the
\Def{completion} of $\Rew$. By Lemma~\ref{lem:degree_confluence},
$\RewContext'$ is confluent. Notice that, for certain inputs $\Rew$,
this semi-algorithm never stops. Notice also that the computed
completion depend on the total order $\leq$ on the binary trees of a
same arity.
\medbreak

>>>>

When $\Rew$ is a terminating but not convergent orientation of $\Congr$,
we shall use a variant of the \Def{Buchberger semi-algorithm} for
operads~\cite[Section 3.7]{DK10} to compute a set of rewrite rules
$\Rew'$ such that, as binary relations $\Rew \subseteq \Rew'$, and
$\Rew'$ is a convergent orientation of $\Congr$. This semi-algorithm
takes as input a finite set of rewrite rules $\Rew$ and outputs the set
of rewrite rules $\Rew'$ satisfying the property stated above. Here is,
step by step, a description of its execution:
\begin{enumerate}[label={(\it\arabic*)}]
  \item Set $\Rew' := \Rew$ and let $\BranchingTrees$ be the set of
    branching trees for $\RewContext$.
  \item \label{item:loop_start_buchberger}
    If $\BranchingTrees$ is empty, the execution stops and the output
    is $\Rew'$.
  \item Otherwise, let $\Tfr$ be the branching tree for $\RewContext'$
    with the minimal degree and the minimal prefix word and remove $\Tfr$
    from $\BranchingTrees$.
  \item Let $\{\Sfr_1, \Sfr_2\}$ be the branching pair for $\Tfr$ such
    that $\Sfr_1$ and $\Sfr_2$ have the minimal prefix words.
  \item Let $\overline{\Sfr_1}$ and $\overline{\Sfr_2}$ be normal forms of
    $\Sfr_1$ and $\Sfr_2$, respectively.
  \item \label{item:new_rewrite_rule_buchberger}
    If $\overline{\Sfr_1}$ is different from $\overline{\Sfr_2}$, add
    to $\Rew'$ the rewrite rule
    \begin{math}
      \max_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}
      \Rew'
      \min_\leq \left\{\overline{\Sfr_1}, \overline{\Sfr_2}\right\}.
    \end{math}
  \item Add to $\BranchingTrees$ all new branching trees of degrees at
    most $2 \Deg(\Rew') - 1$ created by the rewrite rule of
    Step~\ref{item:new_rewrite_rule_buchberger}.
  \item Go to Step~\ref{item:loop_start_buchberger}.
\end{enumerate}
The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is the
\Def{completion} of $\Rew$. By Lemma~\ref{lem:degree_confluence},
$\RewContext'$ is confluent. Notice that, for certain inputs $\Rew$,
this semi-algorithm never stops. Notice also that the computed
completion depend on the total order $\leq$ on the binary trees of a
same arity.
\medbreak
